gtsummary

### 2020-12-09 rmarkdown-gtsummary.Rmd
in progress

```{r}
trial %>%
  imap_dfr(
    ~tibble(
      colname = .y, 
      label = attr(.x, "label"), 
      class = class(.x), 
      values = trial %>% select(.y) %>% distinct() %>% 
        arrange(!!rlang::sym(.y)) %>% slice(1:4) %>% pull(.y) %>% 
        na.omit() %>% {paste("`", ., "`", collapse = ", ")}
    ) %>%
      mutate(
        values = ifelse(length(unique(na.omit(trial[[.y]]))) > 4,
                        paste(values, ", ..."),
                        values) 
      )
  ) %>%
  knitr::kable(caption = "Example data frame, `trial`") 
```

@@

```{r}
tibble::tribble(
  ~Argument,       ~Description,
  "`label`",       "specify the variable labels printed in table",
  "`type`",        "specify the variable type (e.g. continuous, categorical, etc.)",
  "`statistic`",   "change the summary statistics presented",
  "`digits`",      "number of digits the summary statistics will be rounded to",
  "`missing`",     "whether to display a row with the number of missing observations",
  "`missing_text`","text label for the missing number row",
  "`sort`",        "change the sorting of categorical levels by frequency",
  "`percent`",     "print column, row, or cell percentages"
) %>%
  knitr::kable(caption = "`tbl_summary()` function arguments") 
```

>>>>

```{r}
trial %>%
  imap_dfr(
    ~tibble(
      colname = str_glue('`"{.y}"`'), 
      label = attr(.x, "label"), 
      class = class(.x), 
      values = trial %>% select(.y) %>% distinct() %>% 
        arrange(!!rlang::sym(.y)) %>% slice(1:4) %>% pull(.y) %>% 
        na.omit() %>% {paste("`", ., "`", collapse = ", ")}
    ) %>%
      mutate(
        values = ifelse(length(unique(na.omit(trial[[.y]]))) > 4,
                        paste(values, ", ..."),
                        values) 
      )
  ) %>%
  gt(caption = "Example data frame, `trial`") %>%
  fmt_markdown(everything()) %>%
  as_latex() %>%
  as.character() %>%
  readr::write_lines("tbl_trial_desc.tex")
```

@@

```{r}
tibble::tribble(
  ~Argument,       ~Description,
  "`label`",       "specify the variable labels printed in table",
  "`type`",        "specify the variable type (e.g. continuous, categorical, etc.)",
  "`statistic`",   "change the summary statistics presented",
  "`digits`",      "number of digits the summary statistics will be rounded to",
  "`missing`",     "whether to display a row with the number of missing observations",
  "`missing_text`","text label for the missing number row",
  "`sort`",        "change the sorting of categorical levels by frequency",
  "`percent`",     "print column, row, or cell percentages"
)  %>%
  gt(caption = "`tbl_summary()` function arguments") %>%
  fmt_markdown(everything()) %>%
  as_latex() %>%
  as.character() %>%
  readr::write_lines("tbl_tbl_summary_args.tex")

```

### 2020-12-09 tbl_tbl_summary_args.tex
in progress

Table: `tbl_summary()` function arguments

|Argument       |Description                                                      |
|:--------------|:----------------------------------------------------------------|
|`label`        |specify the variable labels printed in table                     |
|`type`         |specify the variable type (e.g. continuous, categorical, etc.)   |
|`statistic`    |change the summary statistics presented                          |
|`digits`       |number of digits the summary statistics will be rounded to       |
|`missing`      |whether to display a row with the number of missing observations |
|`missing_text` |text label for the missing number row                            |
|`sort`         |change the sorting of categorical levels by frequency            |
|`percent`      |print column, row, or cell percentages                           |

>>>>

\captionsetup[table]{labelformat=empty,skip=1pt}
\begin{longtable}{ll}
\toprule
Argument & Description \\ 
\midrule
\texttt{label} & specify the variable labels printed in table \\ 
\texttt{type} & specify the variable type (e.g. continuous, categorical, etc.) \\ 
\texttt{statistic} & change the summary statistics presented \\ 
\texttt{digits} & number of digits the summary statistics will be rounded to \\ 
\texttt{missing} & whether to display a row with the number of missing observations \\ 
\texttt{missing\_text} & text label for the missing number row \\ 
\texttt{sort} & change the sorting of categorical levels by frequency \\ 
\texttt{percent} & print column, row, or cell percentages \\ 
\bottomrule
\end{longtable}

### 2020-12-09 tbl_trial_desc.tex
in progress

\begin{table}

\caption{\label{tab:unnamed-chunk-1}Example data frame, `trial`}
\centering
\begin{tabular}[t]{l|l|l|l}
\hline
colname & label & class & values\\
\hline
trt & Chemotherapy Treatment & character & ` Drug A `, ` Drug B `\\
\hline
age & Age & numeric & ` 6 `, ` 9 `, ` 10 `, ` 17 ` , ...\\
\hline
marker & Marker Level (ng/mL) & numeric & ` 0.003 `, ` 0.005 `, ` 0.013 `, ` 0.015 ` , ...\\
\hline
stage & T Stage & factor & ` T1 `, ` T2 `, ` T3 `, ` T4 `\\
\hline
grade & Grade & factor & ` I `, ` II `, ` III `\\
\hline
response & Tumor Response & integer & ` 0 `, ` 1 `\\
\hline
death & Patient Died & integer & ` 0 `, ` 1 `\\
\hline
ttdeath & Months to Death/Censor & numeric & ` 3.53 `, ` 5.33 `, ` 6.32 `, ` 7.27 ` , ...\\
\hline
\end{tabular}
\end{table}

>>>>

\captionsetup[table]{labelformat=empty,skip=1pt}
\begin{longtable}{clll}
\toprule
colname & label & class & values \\ 
\midrule
\texttt{\textquotedbl{}trt\textquotedbl{}} & Chemotherapy Treatment & character & \texttt{Drug A}, \texttt{Drug B} \\ 
\texttt{\textquotedbl{}age\textquotedbl{}} & Age & numeric & \texttt{6}, \texttt{9}, \texttt{10}, \texttt{17} , ... \\ 
\texttt{\textquotedbl{}marker\textquotedbl{}} & Marker Level (ng/mL) & numeric & \texttt{0.003}, \texttt{0.005}, \texttt{0.013}, \texttt{0.015} , ... \\ 
\texttt{\textquotedbl{}stage\textquotedbl{}} & T Stage & factor & \texttt{T1}, \texttt{T2}, \texttt{T3}, \texttt{T4} \\ 
\texttt{\textquotedbl{}grade\textquotedbl{}} & Grade & factor & \texttt{I}, \texttt{II}, \texttt{III} \\ 
\texttt{\textquotedbl{}response\textquotedbl{}} & Tumor Response & integer & \texttt{0}, \texttt{1} \\ 
\texttt{\textquotedbl{}death\textquotedbl{}} & Patient Died & integer & \texttt{0}, \texttt{1} \\ 
\texttt{\textquotedbl{}ttdeath\textquotedbl{}} & Months to Death/Censor & numeric & \texttt{3.53}, \texttt{5.33}, \texttt{6.32}, \texttt{7.27} , ... \\ 
\bottomrule
\end{longtable}
